\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Update on Overleaf.
uwds tf

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

@@

As previously mentioned, worlds are composite data structures comprising of a
scene graph and a timeline. These data structures are synchronized using
Google's gRPC message passing framework\footnote{http://www.grpc.io/}, ensuring
high throughput, reliability, cross-platform/cross-language support. The \uwds
API is specifically discussed hereafter, section~\ref{api}.

@@

As mentioned in section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitely defined, and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

@@

@@

{\tt uwds tf}

@@

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in Figure \ref{fig|l2torexample}, the user manipulates the physical objects on top of an RFID mat as instructed by the NAO robot.     
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients

>>>>

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}

\usepackage{hyperref}

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

@@

As previously mentioned, worlds are composite data structures comprising of a
scene graph and a timeline. These data structures are synchronized using
Google's gRPC message passing framework\footnote{\url{http://www.grpc.io/}}, ensuring
high throughput, reliability, cross-platform/cross-language support. The \uwds
API is specifically discussed hereafter, section~\ref{api}.

@@

As mentioned in section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitely defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

@@

%%TODO add screenshot of uwds explorer

@@

\uwds is meant to integrate as easily as possible into existing robot
architectures, and interfaces transparently with ROS' TF frame system through
the {\tt uwds tf} client.

The {\tt uwds tf} root client continuously monitor the ROS TF tree, and mirror
TF frames as nodes in a given \uwds world. A node is first created if none
matches a given TF frame, and its transformation is subsequently updated,
mirroring the TF frame. A regular expression can be provided to only mirror a
subset of the TF tree into \uwds.

Currently, the process is unidirectional: the {\tt uwds tf} client performs TF
to \uwds updates, but not the opposite.

@@

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in Figure \ref{fig|l2torexample}, the user manipulates the physical objects on top of an RFID mat as instructed by the NAO robot.

L2TOR \uwds clients:
\subsubsection{Kinect Head Tracker}
\subsubsection{Object RFID tracker}
\subsubsection{NAO model}
\subsubsection{Visibility computation}
\subsubsection{Spatial Relations computation}
\subsubsection{Game/Rules computation}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients
